S1 Appendix

### 2021-02-01 paper/2_final_submission/tranos_ioannides.tex
visualisations

Table \ref{zipf} presents the estimated \(\zeta\) coefficients for the
panel of countries that the second stage of the analysis focuses on
using the UN urban agglomerations data. It becomes evident that there is
considerable variation in the estimates of \(\zeta\) across the
different countries in the sample. Because of the empirically
established heavy upper tail of data for cities and urban
agglomerations, the \(\zeta\) coefficient constitutes a convenient
measure of dispersion. The larger its absolute value, the thinner the
upper tail; equivalently, the larger is the coefficient algebraically,
the heavier the upper tail. This key observation is basis for the second
step of our methodology.

@@

\caption{\label{tab:unnamed-chunk-2}Pareto exponent\label{zipf}}

@@

\multicolumn{20}{l}{\textit{Note: }}\\
\multicolumn{20}{l}{Corrected as per Gabaix and Ibragimov (2011)}\\

@@

\begin{table}[!htbp] \centering 
  \caption{2SLS estimation of equation (3)\label{2sls.global}} 
  \label{} 
\small 
\begin{tabular}{@{\extracolsep{1pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{Pareto exponent 2000-18} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
\hline \\[-1.8ex] 
 Internet users per 100 hab. (log) & 0.001$^{***}$ &  &  &  \\ 
  & (0.0004) &  &  &  \\ 
  Broadband users per 100 hab. (log) &  & 0.002$^{**}$ &  &  \\ 
  &  & (0.001) &  &  \\ 
  Mobile phone users per 100 hab. (log) &  &  & $-$0.007$^{*}$ &  \\ 
  &  &  & (0.004) &  \\ 
  Fixed phone users per 100 hab. (log) &  &  &  & $-$0.001$^{***}$ \\ 
  &  &  &  & (0.0003) \\ 
  Population density (log) & $-$0.827 & $-$1.736 & $-$12.765 & $-$0.828 \\ 
  & (1.841) & (2.622) & (8.326) & (2.262) \\ 
  Government expenditure (\% GDP) & $-$0.0003 & 0.0002 & $-$0.002 & $-$0.0003 \\ 
  & (0.001) & (0.002) & (0.002) & (0.001) \\ 
  Trade (\% of GDP) & 0.0004$^{***}$ & 0.0004$^{*}$ & 0.001 & $-$0.0003 \\ 
  & (0.0001) & (0.0002) & (0.0005) & (0.0002) \\ 
  Non agriculture value added (\% GDP) & 0.0003 & $-$0.0003 & $-$0.001 & $-$0.001 \\ 
  & (0.001) & (0.001) & (0.001) & (0.001) \\ 
  GDP growth & 0.001$^{***}$ & 0.002$^{***}$ & 0.001$^{*}$ & 0.0001 \\ 
  & (0.0004) & (0.001) & (0.001) & (0.0004) \\ 
  GDP per capita (log) & $-$0.023$^{***}$ & 0.003 & 0.034 & $-$0.0003 \\ 
  & (0.007) & (0.012) & (0.038) & (0.011) \\ 
  Population (log) & 0.776 & 1.867 & 12.794 & 0.740 \\ 
  & (1.841) & (2.646) & (8.410) & (2.267) \\ 
  Constant & $-$11.513 & $-$27.468 & $-$180.823 & $-$10.915 \\ 
  & (25.852) & (37.246) & (118.577) & (31.852) \\ 
 \hline \\[-1.8ex] 
Weak instruments & 44.77 & 22.23 & 3.51 & 27.24 \\ 
Wu-Hausman & 3 & 15.96 & 12.26 & 12 \\ 
P-value & 0.08 & 0 & 0 & 0 \\ 
Country fixed effects & Yes & Yes & Yes & Yes \\ 
Yearly fixed effects & Yes & Yes & Yes & Yes \\ 
Observations & 844 & 757 & 865 & 867 \\ 
Adjusted R$^{2}$ & 0.986 & 0.984 & 0.944 & 0.979 \\ 
Residual Std. Error & 0.534 & 0.579 & 1.078 & 0.657 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 & \multicolumn{4}{r}{Robust std. errors in parenthesis} \\ 
 & \multicolumn{4}{r}{IV: Female participation in labour force} \\ 
 & \multicolumn{4}{r}{First stage regressions can be found in S2} \\ 
\end{tabular} 
\end{table}

@@

\begin{table}[!htbp] \centering 
  \caption{2SLS estimation of equation (4) for USA\label{2sls.usa}} 
  \label{} 
\small 
\begin{tabular}{@{\extracolsep{-15pt}}lD{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{2}{c}{\textit{Dependent variable:}} \\ 
\cline{2-3} 
\\[-1.8ex] & \multicolumn{2}{c}{Difference in ranks, 2013-18} \\ 
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)}\\ 
\hline \\[-1.8ex] 
 \% of households w. internet 2013 & 93.908^{***} & 86.712^{***} \\ 
  & (21.028) & (21.085) \\ 
  population 2013 (log) & -0.624 & -0.558 \\ 
  & (0.489) & (0.489) \\ 
  \% of unemployment 2013 & -0.429^{**} & -0.417^{**} \\ 
  & (0.206) & (0.202) \\ 
  \% of white population 2013 & -5.973 & -4.944 \\ 
  & (4.748) & (4.629) \\ 
  income 2013 (log) & -24.364^{***} & -22.207^{***} \\ 
  & (6.541) & (6.437) \\ 
  population density 2013 & -1.110^{***} & -1.101^{***} \\ 
  & (0.379) & (0.368) \\ 
  \% of employment in service 2011 & -0.117 & -0.100 \\ 
  & (0.084) & (0.082) \\ 
  commute in minutes 2013 & 0.367^{*} & 0.349^{*} \\ 
  & (0.192) & (0.188) \\ 
  Constant & 196.828^{***} & 177.500^{***} \\ 
  & (60.591) & (59.487) \\ 
 \hline \\[-1.8ex] 
Weak instruments & 114.85 & 62.05 \\ 
Wu-Hausman & 5.23 & 3.58 \\ 
P-value & 0.02 & 0.06 \\ 
Sargan &  & 5.65 \\ 
P-value &  & 0.02 \\ 
Observations & \multicolumn{1}{c}{443} & \multicolumn{1}{c}{443} \\ 
Adjusted R$^{2}$ & \multicolumn{1}{c}{0.061} & \multicolumn{1}{c}{0.080} \\ 
Residual Std. Error & \multicolumn{1}{c}{7.819} & \multicolumn{1}{c}{7.740} \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 & \multicolumn{2}{r}{Robust Std. Errors in parenthesis} \\ 
 & \multicolumn{2}{r}{IVs: (1) Bachelors degree per hab. in 2005} \\ 
 & \multicolumn{2}{r}{IVs: (2) Bachelors degree per hab. in 2005, Commute, minutes, 2005} \\ 
 & \multicolumn{2}{r}{First stage regressions can be found in S2} \\ 
\end{tabular} 
\end{table}

@@

\begin{table}[!htbp] \centering 
  \caption{2SLS estimation of equation (4) for the UK\label{2sls.uk}} 
  \label{} 
\small 
\begin{tabular}{@{\extracolsep{5pt}}lcc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{2}{c}{\textit{Dependent variable:}} \\ 
\cline{2-3} 
\\[-1.8ex] & \multicolumn{2}{c}{Difference in ranks, 2011-18} \\ 
\\[-1.8ex] & (1) & (2)\\ 
\hline \\[-1.8ex] 
 download speed, 2011 (log) & 43.058$^{***}$ & 47.226$^{***}$ \\ 
  & (11.727) & (6.298) \\ 
  population, 2011 (log) & $-$1.735 & $-$2.451$^{*}$ \\ 
  & (2.327) & (1.389) \\ 
  broadband tests per capita, 2011 & $-$6.658 & $-$5.763 \\ 
  & (12.159) & (12.263) \\ 
  \% of unemployment, 2011 & $-$93.185 & $-$89.366 \\ 
  & (60.397) & (59.332) \\ 
  \% of British population, 2011 & $-$36.963$^{**}$ & $-$38.269$^{**}$ \\ 
  & (17.921) & (17.631) \\ 
  population density, 2011 & $-$0.003 & $-$0.010 \\ 
  & (0.144) & (0.147) \\ 
  \% of people working from home, 2011 & $-$92.525$^{**}$ & $-$93.787$^{**}$ \\ 
  & (40.412) & (40.729) \\ 
  employment in service, 2011 (\%) & $-$47.395$^{*}$ & $-$48.132$^{*}$ \\ 
  & (28.089) & (28.448) \\ 
  Constant & $-$260.358$^{***}$ & $-$286.509$^{***}$ \\ 
  & (81.193) & (51.613) \\ 
 \hline \\[-1.8ex] 
Weak instruments & 6.98 & 42.03 \\ 
Wu-Hausman & 8.08 & 40.8 \\ 
P-value & 0 & 0 \\ 
Sargan &  & 0.02 \\ 
P-value &  & 0.9 \\ 
Observations & 3,032 & 3,032 \\ 
Adjusted R$^{2}$ & $-$0.069 & $-$0.096 \\ 
Residual Std. Error & 57.001 & 57.721 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 & \multicolumn{2}{r}{Robust std. errors in parenthesis} \\ 
 & \multicolumn{2}{r}{IVs: (1) N.r of universities} \\ 
 & \multicolumn{2}{r}{IVs: (2) N. of universities, N. of broadband tests, 2011} \\ 
 & \multicolumn{2}{r}{First stage regressions can be found in S2} \\ 
\end{tabular} 
\end{table}

>>>>

Table \ref{zipf} presents the estimated \(\zeta\) coefficients for the
panel of countries that the second stage of the analysis focuses on
using the UN urban agglomerations data. More detailed and interactive
visualisations can be found in Appendix S2. It becomes evident that
there is considerable variation in the estimates of \(\zeta\) across the
different countries in the sample. Because of the empirically
established heavy upper tail of data for cities and urban
agglomerations, the \(\zeta\) coefficient constitutes a convenient
measure of dispersion. The larger its absolute value, the thinner the
upper tail; equivalently, the larger is the coefficient algebraically,
the heavier the upper tail. This key observation is basis for the second
step of our methodology.

@@

\caption{\label{tab:unnamed-chunk-2}Pareto exponents\label{zipf}}

@@

\multicolumn{20}{l}{\rule{0pt}{1em}\textit{Note: }}\\
\multicolumn{20}{l}{\rule{0pt}{1em}Corrected as per Gabaix and Ibragimov (2011)}\\

@@

\begin{table}[!htbp] \centering 
  \caption{2SLS estimation of equation (3)\label{2sls.global}} 
  \label{} 
\small 
\begin{tabular}{@{\extracolsep{1pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{Pareto exponent 2000-18} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
\hline \\[-1.8ex] 
 Internet users per 100 hab. (log) & 0.001$^{***}$ &  &  &  \\ 
  & (0.0004) &  &  &  \\ 
  Broadband users per 100 hab. (log) &  & 0.002$^{**}$ &  &  \\ 
  &  & (0.001) &  &  \\ 
  Mobile phone users per 100 hab. (log) &  &  & $-$0.007$^{*}$ &  \\ 
  &  &  & (0.004) &  \\ 
  Fixed phone users per 100 hab. (log) &  &  &  & $-$0.001$^{***}$ \\ 
  &  &  &  & (0.0003) \\ 
  Population density (log) & $-$0.827 & $-$1.736 & $-$12.765 & $-$0.828 \\ 
  & (1.841) & (2.622) & (8.326) & (2.262) \\ 
  Government expenditure (\% GDP) & $-$0.0003 & 0.0002 & $-$0.002 & $-$0.0003 \\ 
  & (0.001) & (0.002) & (0.002) & (0.001) \\ 
  Trade (\% of GDP) & 0.0004$^{***}$ & 0.0004$^{*}$ & 0.001 & $-$0.0003 \\ 
  & (0.0001) & (0.0002) & (0.0005) & (0.0002) \\ 
  Non agriculture value added (\% GDP) & 0.0003 & $-$0.0003 & $-$0.001 & $-$0.001 \\ 
  & (0.001) & (0.001) & (0.001) & (0.001) \\ 
  GDP growth & 0.001$^{***}$ & 0.002$^{***}$ & 0.001$^{*}$ & 0.0001 \\ 
  & (0.0004) & (0.001) & (0.001) & (0.0004) \\ 
  GDP per capita (log) & $-$0.023$^{***}$ & 0.003 & 0.034 & $-$0.0003 \\ 
  & (0.007) & (0.012) & (0.038) & (0.011) \\ 
  Population (log) & 0.776 & 1.867 & 12.794 & 0.740 \\ 
  & (1.841) & (2.646) & (8.410) & (2.267) \\ 
  Constant & $-$11.513 & $-$27.468 & $-$180.823 & $-$10.915 \\ 
  & (25.852) & (37.246) & (118.577) & (31.852) \\ 
 \hline \\[-1.8ex] 
Weak instruments & 44.77 & 22.23 & 3.51 & 27.24 \\ 
Wu-Hausman & 3 & 15.96 & 12.26 & 12 \\ 
P-value & 0.08 & 0 & 0 & 0 \\ 
Country fixed effects & Yes & Yes & Yes & Yes \\ 
Yearly fixed effects & Yes & Yes & Yes & Yes \\ 
Observations & 844 & 757 & 865 & 867 \\ 
Adjusted R$^{2}$ & 0.986 & 0.984 & 0.944 & 0.979 \\ 
Residual Std. Error & 0.534 & 0.579 & 1.078 & 0.657 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 & \multicolumn{4}{r}{Robust std. errors in parenthesis} \\ 
 & \multicolumn{4}{r}{IV: Female participation in labour force} \\ 
 & \multicolumn{4}{r}{First stage regressions can be found in S3} \\ 
\end{tabular} 
\end{table}

@@

\begin{table}[!htbp] \centering 
  \caption{2SLS estimation of equation (4) for USA\label{2sls.usa}} 
  \label{} 
\small 
\begin{tabular}{@{\extracolsep{-15pt}}lD{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{2}{c}{\textit{Dependent variable:}} \\ 
\cline{2-3} 
\\[-1.8ex] & \multicolumn{2}{c}{Difference in ranks, 2013-18} \\ 
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)}\\ 
\hline \\[-1.8ex] 
 \% of households w. internet 2013 & 93.908^{***} & 86.712^{***} \\ 
  & (21.028) & (21.085) \\ 
  population 2013 (log) & -0.624 & -0.558 \\ 
  & (0.489) & (0.489) \\ 
  \% of unemployment 2013 & -0.429^{**} & -0.417^{**} \\ 
  & (0.206) & (0.202) \\ 
  \% of white population 2013 & -5.973 & -4.944 \\ 
  & (4.748) & (4.629) \\ 
  income 2013 (log) & -24.364^{***} & -22.207^{***} \\ 
  & (6.541) & (6.437) \\ 
  population density 2013 & -1.110^{***} & -1.101^{***} \\ 
  & (0.379) & (0.368) \\ 
  \% of employment in service 2011 & -0.117 & -0.100 \\ 
  & (0.084) & (0.082) \\ 
  commute in minutes 2013 & 0.367^{*} & 0.349^{*} \\ 
  & (0.192) & (0.188) \\ 
  Constant & 196.828^{***} & 177.500^{***} \\ 
  & (60.591) & (59.487) \\ 
 \hline \\[-1.8ex] 
Weak instruments & 114.85 & 62.05 \\ 
Wu-Hausman & 5.23 & 3.58 \\ 
P-value & 0.02 & 0.06 \\ 
Sargan &  & 5.65 \\ 
P-value &  & 0.02 \\ 
Observations & \multicolumn{1}{c}{443} & \multicolumn{1}{c}{443} \\ 
Adjusted R$^{2}$ & \multicolumn{1}{c}{0.061} & \multicolumn{1}{c}{0.080} \\ 
Residual Std. Error & \multicolumn{1}{c}{7.819} & \multicolumn{1}{c}{7.740} \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 & \multicolumn{2}{r}{Robust Std. Errors in parenthesis} \\ 
 & \multicolumn{2}{r}{IVs: (1) Bachelors degree per hab. in 2005} \\ 
 & \multicolumn{2}{r}{IVs: (2) Bachelors degree per hab. in 2005, Commute, minutes, 2005} \\ 
 & \multicolumn{2}{r}{First stage regressions can be found in S3} \\ 
\end{tabular} 
\end{table}

@@

\begin{table}[!htbp] \centering 
  \caption{2SLS estimation of equation (4) for the UK\label{2sls.uk}} 
  \label{} 
\small 
\begin{tabular}{@{\extracolsep{5pt}}lcc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{2}{c}{\textit{Dependent variable:}} \\ 
\cline{2-3} 
\\[-1.8ex] & \multicolumn{2}{c}{Difference in ranks, 2011-18} \\ 
\\[-1.8ex] & (1) & (2)\\ 
\hline \\[-1.8ex] 
 download speed, 2011 (log) & 43.058$^{***}$ & 47.226$^{***}$ \\ 
  & (11.727) & (6.298) \\ 
  population, 2011 (log) & $-$1.735 & $-$2.451$^{*}$ \\ 
  & (2.327) & (1.389) \\ 
  broadband tests per capita, 2011 & $-$6.658 & $-$5.763 \\ 
  & (12.159) & (12.263) \\ 
  \% of unemployment, 2011 & $-$93.185 & $-$89.366 \\ 
  & (60.397) & (59.332) \\ 
  \% of British population, 2011 & $-$36.963$^{**}$ & $-$38.269$^{**}$ \\ 
  & (17.921) & (17.631) \\ 
  population density, 2011 & $-$0.003 & $-$0.010 \\ 
  & (0.144) & (0.147) \\ 
  \% of people working from home, 2011 & $-$92.525$^{**}$ & $-$93.787$^{**}$ \\ 
  & (40.412) & (40.729) \\ 
  employment in service, 2011 (\%) & $-$47.395$^{*}$ & $-$48.132$^{*}$ \\ 
  & (28.089) & (28.448) \\ 
  Constant & $-$260.358$^{***}$ & $-$286.509$^{***}$ \\ 
  & (81.193) & (51.613) \\ 
 \hline \\[-1.8ex] 
Weak instruments & 6.98 & 42.03 \\ 
Wu-Hausman & 8.08 & 40.8 \\ 
P-value & 0 & 0 \\ 
Sargan &  & 0.02 \\ 
P-value &  & 0.9 \\ 
Observations & 3,032 & 3,032 \\ 
Adjusted R$^{2}$ & $-$0.069 & $-$0.096 \\ 
Residual Std. Error & 57.001 & 57.721 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 & \multicolumn{2}{r}{Robust std. errors in parenthesis} \\ 
 & \multicolumn{2}{r}{IVs: (1) N.r of universities} \\ 
 & \multicolumn{2}{r}{IVs: (2) N. of universities, N. of broadband tests, 2011} \\ 
 & \multicolumn{2}{r}{First stage regressions can be found in S3} \\ 
\end{tabular} 
\end{table}

### 2021-02-01 src/s1.Rmd
visualisations

---
title: "S1 Appendix"
author: ""
output: pdf_document
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_dir = "../paper/2_resubmission")
  })
---

@@

# This is the project path
# path <- find_rstudio_root_file()

load("C:/Users/nw19521/OneDrive - University of Bristol/projects/Ioannides/ict.un.us.uk/data/data_inter/UN.RData")
```

>>>>

---
title: "S1 Appendix"
author: ""
output: pdf_document
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_dir = "../paper/2_final_submission")
  })
---

@@

# This is the project path
path <- find_rstudio_root_file()

# load data
path <- find_rstudio_root_file()
path.un <- paste0(path, "/data/data_inter/UN.RData")

load(path.un)
```
